R for Clinical Study Reports and Submission

### 2022-12-07 tlf-ae-spec.Rmd
automate rtf to pdf conversion
TLF chapters PDF output patch - add `\mainmatter` and make `out.height` HTML-specific as LaTeX does not support px as a unit

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/tlf_spec_ae.pdf")
```

@@

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/tlf_spec_ae.pdf")
```

>>>>

```{r, out.width = "100%", out.height = if (knitr::is_html_output()) "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/tlf_spec_ae.pdf")
```

@@

```{r, include=FALSE}
rtf2pdf("tlf/tlf_spec_ae.rtf")
```

```{r, out.width = "100%", out.height = if (knitr::is_html_output()) "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/tlf_spec_ae.pdf")
```

### 2022-12-07 tlf-overview.Rmd
minor updates
TLF chapters PDF output patch - add `\mainmatter` and make `out.height` HTML-specific as LaTeX does not support px as a unit

@@

::: {.rmdnote}
There are other R packages to create TLFs in ASCII, RTF and Word format.
For example, `rtables`, `huxtable`, `pharmaRTF`, `gt`, `officer`, `flextable` etc.
Here we focus on `r2rtf` to illustrate the concept.  
Reader is encouraged to explore other R packages to find the proper tools to fit your purpose. 
:::

@@

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae1.pdf")
```

@@

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae2.pdf")
```

@@

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae3.pdf")
```

@@

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae5.pdf")
```

@@

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae7.pdf")
```

>>>>

\mainmatter

@@

::: {.rmdnote}
There are other R packages to create TLFs in ASCII, RTF and Word format.
For example, `rtables`, `huxtable`, `pharmaRTF`, `gt`, `officer`, `flextable` etc.
Here we focus on `r2rtf` to illustrate the concept.  
Readers are encouraged to explore other R packages to find the proper tools to fit your purpose. 
:::

@@

```{r, out.width = "100%", out.height = if (knitr::is_html_output()) "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae1.pdf")
```

@@

```{r, out.width = "100%", out.height = if (knitr::is_html_output()) "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae2.pdf")
```

@@

```{r, out.width = "100%", out.height = if (knitr::is_html_output()) "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae3.pdf")
```

@@

```{r, out.width = "100%", out.height = if (knitr::is_html_output()) "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae5.pdf")
```

@@

```{r, out.width = "100%", out.height = if (knitr::is_html_output()) "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/intro-ae7.pdf")
```
